# Introduction

## flowCore intro

There is no better way to learn than to do. Here we learn how to analyze FC data using a popular bioconductor package called [flowCore](https://www.bioconductor.org/packages/release/bioc/html/flowCore.html).

In this chapter, we will try to cover all the major concepts from [How-To-flowCore](https://www.bioconductor.org/packages/release/bioc/vignettes/flowCore/inst/doc/HowTo-flowCore.pdf). 

flowCore package is that of using a standardized representation that will insure compatibility with existing technologies for data analysis and will support collaboration and interoperability of new methods as they are developed. flowCore adapts `expressionSet` and `AnnotateDataFrame` structures which are familiar to most Bioconductor users.

In the following articles, I try to cover the main steps of preprocessing: compensation, transformation, filtering.

```{r install flowCore, warning=FALSE}
BiocManager::install("flowCore")
```

Load required library
```{r}
library(flowCore)
```

## reading an FCS file into a flowFrame
```{r}
file.name <- system.file("extdata", "0877408774.B08",
                         package="flowCore")
x <- read.FCS(file.name, transformation=FALSE) # default is linearize transformation
summary(x)
```

```{r}
head(x)
```

```{r}
str(x)
```


```{r}
keyword(x, c("$P1E", "$P2E", "$P3E", "$P4E"))
```

The default "linearize" transformation option will convert these to, effectively, have a $PnE value of "0,0":
```{r}
summary(read.FCS(file.name))
```

scale transformation
```{r}
summary(read.FCS(file.name, transformation="scale"))
```

Another parameter of interest is the alter.names parameter, which will convert the parameter names into more "R friendly" qauivalents, usually by replacing "-" with ".";
```{r}
read.FCS(file.name, alter.names=TRUE)
```



